Experiment 2 of 4

### 2018-08-02 experiments/B_pilot_2/writeup/e1.Rmd
massive restructuring Aug 2018

@@

```{r loadLibraries, message=FALSE, echo=FALSE, cache=FALSE}
library(knitr); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); source('summarySEwithin2.R') 
```

@@

```{r separateDataFramesForRTandErrorAnalyses, echo=TRUE, cache=FALSE}
rawdata <- read.table('data.txt', sep=' ')
rtdata <- subset(rawdata, error==FALSE)
erdata <- rawdata
```

@@

```{r computeSummariesForGraphs, cache=TRUE}
rtdataplot1 = summarySEwithin2(rtdata,  measurevar="logrt",  withinvars=c("Vgn","Gap"), idvar="subject")
erdataplot1 <- summarySEwithin2(erdata, measurevar="error", withinvars=c("Vgn","Gap"), idvar="subject")
```

```{r rtplot, echo = FALSE}
dodge=.06
rtplot = ggplot(rtdataplot1, aes(y=logrtNormed, x=Gap, group=Vgn, fill=Vgn, shape=Vgn, ymin=logrtNormed-ci, ymax=logrtNormed+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.3, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=2, position=position_dodge(dodge)) +
  ggtitle("Response time") + 
  ylab("Respone time (log (ms))") + 
  xlab("Gap Size") +
  scale_fill_grey(name=element_blank(), start=0, end=1, guide=FALSE) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() ) +
  theme(aspect.ratio=1) + xlab("")
```

>>>>

<!-- no wrap table entries on their white space -->

<style>
table {
  white-space: nowrap;
}
</style>

@@

```{r loadLibraries, message=FALSE, echo=FALSE, cache=FALSE}
library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); source('summarySEwithin2.R') 
```

```{r tidyr, echo=FALSE, message=FALSE}
library(tidyr)
```

```{r rawdata, cache=FALSE}
rawdata <- read.table('data.txt', sep=' ')
rawdata %>% head() %>% kable()
```

@@

```{r separateDataFramesForRTandErrorAnalyses, echo=TRUE, cache=FALSE}
rtdata <- subset(rawdata, error==FALSE)
erdata <- rawdata
```

There were `r nrow(rawdata)` trials; and `r  nrow(subset(rawdata,error==TRUE))` error trials, representing 
`r round(nrow(subset(rawdata,error==TRUE))/nrow(rawdata) * 100, 1)`% of the raw data.

@@

```{r computeSummariesForGraphs, cache=FALSE}
rtdataplot1 = summarySEwithin2(rtdata,  measurevar="logrt",  withinvars=c("Vgn","Gap"), idvar="subject")
erdataplot1 <- summarySEwithin2(erdata, measurevar="error", withinvars=c("Vgn","Gap"), idvar="subject")
```

```{r rtplot, echo=FALSE}
dodge=.06
rtplot = ggplot(rtdataplot1, aes(y=logrtNormed, x=Gap, group=Vgn, fill=Vgn, shape=Vgn, ymin=logrtNormed-ci, ymax=logrtNormed+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.3, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=2, position=position_dodge(dodge)) +
  ggtitle("Response time") + 
  ylab("Respone time (log (ms))") + 
  xlab("Gap Size") +
  scale_fill_grey(name=element_blank(), start=0, end=1, guide=FALSE) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() ) +
  theme(aspect.ratio=1) + xlab("")
```

### 2018-08-02 experiments/C_exp_1/archive/data_wrangling.Rmd
massive restructuring Aug 2018

---
title: "Experiment 3 of 4"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---  
# Experiment 3

```{r docOpts}
library(knitr)
```

```{r loadLibraries}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(reshape))
suppressPackageStartupMessages(library(lattice))
suppressPackageStartupMessages(library(LMERConvenienceFunctions))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(require(languageR))
```

# Experiment Structure
Each subject saw 192 trials, being 3 cycles of 64 trials. There were 38 participants. There were 7296 rows in the full data set.

# Trial Procedure
The procedure for each trial was as follows. First an instruction that was a referring expression was presented until participants dismissed it with a key press. Then the squares with dots were presented until the participant responded with a key press, with a 60 second timeout if they did not respond.

# Prepare the data
Source additional R files with functions for computing confidence intervals.

```{r sourceFunctions}
source("functions/CIfunctions.R")
```

Get data.

```{r readdata}
dat <- read.delim("data/allresults.txt", stringsAsFactors = FALSE)

# declare local variables
number_of_valid_subjects <- 38
number_of_rows <- 7296
number_of_trials_per_subject <- number_of_rows / number_of_valid_subjects # 192

# sort out borderline responses into expected near and far
# How many squares in the square they chose? 
dat$RESPONSE <- as.character(dat$RESPONSE)
for (row in 1 : nrow(dat) ) {
  switch(dat[row,'RESPONSE'],
         'LEFT' = {dat[row, 'choice'] <- dat[row, 'Left']},
         'MIDDLE' = {dat[row, 'choice'] <- dat[row, 'Mid']},
         'RIGHT' = {dat[row, 'choice'] <- dat[row, 'Right']}         
  )
}
dat$crossed=paste('Con',dat$Condition,':Quan',dat$Quantity,':Item',dat$Item,sep="")

dat[dat$crossed=='Con1:Quan1:Item1', 'ResponseExpected'] <-  6 
dat[dat$crossed=='Con1:Quan1:Item1', 'ResponseNear']     <- 15  
dat[dat$crossed=='Con1:Quan1:Item1', 'ResponseFar']      <- 24

dat[dat$crossed=='Con1:Quan1:Item2', 'ResponseExpected'] <- 16
dat[dat$crossed=='Con1:Quan1:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con1:Quan1:Item2', 'ResponseFar']      <- 34

dat[dat$crossed=='Con1:Quan1:Item3', 'ResponseExpected'] <- 26
dat[dat$crossed=='Con1:Quan1:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con1:Quan1:Item3', 'ResponseFar']      <- 44

dat[dat$crossed=='Con1:Quan1:Item4', 'ResponseExpected'] <- 36
dat[dat$crossed=='Con1:Quan1:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con1:Quan1:Item4', 'ResponseFar']      <- 54

dat[dat$crossed=='Con1:Quan2:Item1', 'ResponseExpected'] <- 24
dat[dat$crossed=='Con1:Quan2:Item1', 'ResponseNear']     <- 15 
dat[dat$crossed=='Con1:Quan2:Item1', 'ResponseFar']      <-  6

dat[dat$crossed=='Con1:Quan2:Item2', 'ResponseExpected'] <- 34
dat[dat$crossed=='Con1:Quan2:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con1:Quan2:Item2', 'ResponseFar']      <- 16

dat[dat$crossed=='Con1:Quan2:Item3', 'ResponseExpected'] <- 44
dat[dat$crossed=='Con1:Quan2:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con1:Quan2:Item3', 'ResponseFar']      <- 26

dat[dat$crossed=='Con1:Quan2:Item4', 'ResponseExpected'] <- 54
dat[dat$crossed=='Con1:Quan2:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con1:Quan2:Item4', 'ResponseFar']      <- 36

dat[dat$crossed=='Con2:Quan1:Item1', 'ResponseExpected'] <-  6 
dat[dat$crossed=='Con2:Quan1:Item1', 'ResponseNear']     <- 15  
dat[dat$crossed=='Con2:Quan1:Item1', 'ResponseFar']      <- 24

dat[dat$crossed=='Con2:Quan1:Item2', 'ResponseExpected'] <- 16
dat[dat$crossed=='Con2:Quan1:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con2:Quan1:Item2', 'ResponseFar']      <- 34

dat[dat$crossed=='Con2:Quan1:Item3', 'ResponseExpected'] <- 26
dat[dat$crossed=='Con2:Quan1:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con2:Quan1:Item3', 'ResponseFar']      <- 44

dat[dat$crossed=='Con2:Quan1:Item4', 'ResponseExpected'] <- 36
dat[dat$crossed=='Con2:Quan1:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con2:Quan1:Item4', 'ResponseFar']      <- 54

dat[dat$crossed=='Con2:Quan2:Item1', 'ResponseExpected'] <- 24
dat[dat$crossed=='Con2:Quan2:Item1', 'ResponseNear']     <- 15 
dat[dat$crossed=='Con2:Quan2:Item1', 'ResponseFar']      <-  6

dat[dat$crossed=='Con2:Quan2:Item2', 'ResponseExpected'] <- 34
dat[dat$crossed=='Con2:Quan2:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con2:Quan2:Item2', 'ResponseFar']      <- 16

dat[dat$crossed=='Con2:Quan2:Item3', 'ResponseExpected'] <- 44
dat[dat$crossed=='Con2:Quan2:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con2:Quan2:Item3', 'ResponseFar']      <- 26

dat[dat$crossed=='Con2:Quan2:Item4', 'ResponseExpected'] <- 54
dat[dat$crossed=='Con2:Quan2:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con2:Quan2:Item4', 'ResponseFar']      <- 36

dat[dat$crossed=='Con3:Quan1:Item1', 'ResponseExpected'] <-  6 
dat[dat$crossed=='Con3:Quan1:Item1', 'ResponseNear']     <- 15  
dat[dat$crossed=='Con3:Quan1:Item1', 'ResponseFar']      <- 24

dat[dat$crossed=='Con3:Quan1:Item2', 'ResponseExpected'] <- 16
dat[dat$crossed=='Con3:Quan1:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con3:Quan1:Item2', 'ResponseFar']      <- 34

dat[dat$crossed=='Con3:Quan1:Item3', 'ResponseExpected'] <- 26
dat[dat$crossed=='Con3:Quan1:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con3:Quan1:Item3', 'ResponseFar']      <- 44

dat[dat$crossed=='Con3:Quan1:Item4', 'ResponseExpected'] <- 36
dat[dat$crossed=='Con3:Quan1:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con3:Quan1:Item4', 'ResponseFar']      <- 54

dat[dat$crossed=='Con3:Quan2:Item1', 'ResponseExpected'] <- 24
dat[dat$crossed=='Con3:Quan2:Item1', 'ResponseNear']     <- 15 
dat[dat$crossed=='Con3:Quan2:Item1', 'ResponseFar']      <-  6

dat[dat$crossed=='Con3:Quan2:Item2', 'ResponseExpected'] <- 34
dat[dat$crossed=='Con3:Quan2:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con3:Quan2:Item2', 'ResponseFar']      <- 16

dat[dat$crossed=='Con3:Quan2:Item3', 'ResponseExpected'] <- 44
dat[dat$crossed=='Con3:Quan2:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con3:Quan2:Item3', 'ResponseFar']      <- 26

dat[dat$crossed=='Con3:Quan2:Item4', 'ResponseExpected'] <- 54
dat[dat$crossed=='Con3:Quan2:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con3:Quan2:Item4', 'ResponseFar']      <- 36

dat[dat$crossed=='Con4:Quan1:Item1', 'ResponseExpected'] <-  6 
dat[dat$crossed=='Con4:Quan1:Item1', 'ResponseNear']     <- 15  
dat[dat$crossed=='Con4:Quan1:Item1', 'ResponseFar']      <- 24

dat[dat$crossed=='Con4:Quan1:Item2', 'ResponseExpected'] <- 16
dat[dat$crossed=='Con4:Quan1:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con4:Quan1:Item2', 'ResponseFar']      <- 34

dat[dat$crossed=='Con4:Quan1:Item3', 'ResponseExpected'] <- 26
dat[dat$crossed=='Con4:Quan1:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con4:Quan1:Item3', 'ResponseFar']      <- 44

dat[dat$crossed=='Con4:Quan1:Item4', 'ResponseExpected'] <- 36
dat[dat$crossed=='Con4:Quan1:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con4:Quan1:Item4', 'ResponseFar']      <- 54

dat[dat$crossed=='Con4:Quan2:Item1', 'ResponseExpected'] <- 24
dat[dat$crossed=='Con4:Quan2:Item1', 'ResponseNear']     <- 15 
dat[dat$crossed=='Con4:Quan2:Item1', 'ResponseFar']      <-  6

dat[dat$crossed=='Con4:Quan2:Item2', 'ResponseExpected'] <- 34
dat[dat$crossed=='Con4:Quan2:Item2', 'ResponseNear']     <- 25  
dat[dat$crossed=='Con4:Quan2:Item2', 'ResponseFar']      <- 16

dat[dat$crossed=='Con4:Quan2:Item3', 'ResponseExpected'] <- 44
dat[dat$crossed=='Con4:Quan2:Item3', 'ResponseNear']     <- 35
dat[dat$crossed=='Con4:Quan2:Item3', 'ResponseFar']      <- 26

dat[dat$crossed=='Con4:Quan2:Item4', 'ResponseExpected'] <- 54
dat[dat$crossed=='Con4:Quan2:Item4', 'ResponseNear']     <- 45
dat[dat$crossed=='Con4:Quan2:Item4', 'ResponseFar']      <- 36

dat$isResponseExpected <- dat$choice == dat$ResponseExpected
dat$isResponseNear <- dat$choice == dat$ResponseNear
dat$isResponseFar <- dat$choice == dat$ResponseFar

for ( row in 1:nrow(dat) ) {
  dat[row, 'switchResponse'] <- 
    ifelse(dat[row, 'isResponseExpected']==TRUE, 'Expected', 
           ifelse(dat[row, 'isResponseNear']==TRUE, 'Near', 'Far') ) 
}

@@

# TRIAL
# Trial for subject, 1 to 192
dat$Trial = rep(x = 1:number_of_trials_per_subject, times = number_of_valid_subjects)

@@

dat$Selection = ""
dat[dat$Condition %in% c(1,2), "Selection"] <- "matching"
dat[dat$Condition %in% c(3,4), "Selection"] <- "comparison"
dat$Selection.sum <- ifelse(dat$Selection=="matching", .5, -.5)
dat$Selection <- as.factor(dat$Selection)

# remove one zero RT by replacing with NA
dat$RT[dat$RT==0]<-NA

@@

# INSTRUCTION
# add number of characters in the instruction # 29 30 34 36 38
dat$nchar_instr = nchar(as.character(dat$Instruction))
dat$nchar_instr_scaled = as.vector(scale(nchar(as.character(dat$Instruction)), scale=TRUE))

@@

# save dat as dat.Rda
# This data set contains *all* trials including impossible trials and is mainly for graphs comparing different removals
save(dat, file="dat.Rda")

 # lose impossible trials
  dd <- dat
  dd$RT[dd$RT == 1 ] <- NA
  dd$RT[dd$RT > 40000 ] <- NA
  dd <- dd[complete.cases(dd),]
  row.names(dd) <- NULL

@@

# save dd as dd.Rda
# This data set non-impossible trials and renamed/recomputed variables
save(dd, file="dd.Rda")
```

Check the distribution of the trimmed data to see if a transformation is suggested. Log transformation seems to be best so we adopt that for the rest of the analyses.

```{r boxplot subjects and items}
load("dd.Rda")
# allow reference to transformation
subdata = melt(dd,
               measure.vars=c("RT_Rec", "RT_RecSqt", "RT_log", "RT_raw"),
               variable.name="transformation",
               value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ variable, scales="free", ncol=4) +
  geom_boxplot(aes(y=value, x=Item, col="Items")) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects")) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio=1, panel.grid=element_blank()) + 
  scale_colour_manual("",values=c("Items"="red","Subjects"="blue")) +
  xlab("") + ylab("")
```

```{r load_dd}
load("dd.Rda")
```

```{r do_lmer}
v5 <- lmer(data=dd, 
           RT_RecSqt ~ 
             c_Vag + Selection.sum + c_Qty + c_Ord + 
             Selection.sum:c_Vag:c_Qty +
             item_mean_ratio + 
             s_Trl +
             RTprev_RecSqt +
             nchar_instr +
             (1+c_Vag + Selection.sum + c_Qty + c_Ord|Subject)
)
```

```{r summary_lmer}
summary(v5)
```

```{r R2}
cat("R^2")
cor(fitted(v5), dd$RT_RecSqt)^2
```

```{r plotLMER}
par(mfrow=c(2,5))
plotLMER.fnc(v5)
```

Plot model coefficients and ci's

```{r coeff}
par(las=2, mar=c(14,6,1,1))
y=as.data.frame(summary(v5)$coef[-1,1]) # estimates, without intercept
q=confint(v5)[-c(1,2,3),]
y=cbind(y,q)
plot(y[,1], ylim=range(y[,1],y[,2],y[,3]), xaxt="n", xlab="", ylab="estimate\n",  pch='-', cex=2)
segments(x0=1:nrow(y), x1=1:nrow(y), y[,2], y[,3])
abline(h=0)
axis(1, labels=row.names(y), at=1:nrow(y), srt=45)
grid()
```

Model criticism baayen plots

```{r baayenplots, fig.width=9, fig.height=3}
# Baayen 4-plot model criticism

par(mfrow=c(1,4), pty='s')
# create scaled residuals
v5$rstand = as.vector(scale(resid(v5)))
# plot scaled residuals density
plot(density(v5$rstand))
# plot sample quantiles versus theoretical quantiles
qqnorm(v5$rstand, cex=.5)
qqline(v5$rstand)
# plot standardised residuals versus fitted values
plot(v5$rstand ~ fitted(v5), pch='.')
# absolute standardised residuals greater than 2.5 are candidates for being outliers, the abline identifies them on the plot
abline(h=c(-2.5,2.5))
# create dffits
dffits=abs(resid(v5, "dffits"))
# plot dffits
plot(dffits, type='h')
```

>>>>

Get the data if file dat.Rda does not already exist.

```{r, get_the_data}
# if the output file dat.Rda already exists then load it, else do data wrangling
if( file.exists('dat.Rda') ) load('dat.Rda') else {

  # source required data wrangling functions
  source('functions/classifyResponse.R')
  source('functions/gatherData.R')

  # declare local variables
  number_of_valid_subjects <- 30
  number_of_rows <- 7680 # 7680
  number_of_trials_per_subject <- number_of_rows / number_of_valid_subjects # 256

    ## call user-defined functions

  # collect all individual subject files into one data frame
  dat <- gatherData(number_of_valid_subjects)

  # classify the response as expected, near, or far
  dat <- classifyResponse(dat)

@@

  # TRIAL
  # Trial for subject, 1 to 256
  dat$Trial = rep(x = 1:number_of_trials_per_subject, times = number_of_valid_subjects)

@@

  # NUMBER
  # Create a factor coding for Number use
  dat[ dat$Condition==1 , 'Number'] <- 'Numeric'
  dat[ dat$Condition==2 , 'Number'] <- 'Numeric'
  dat[ dat$Condition==3 , 'Number'] <- 'Verbal'
  dat[ dat$Condition==4 , 'Number'] <- 'Verbal'
  dat$Number <- as.factor(dat$Number)

  # manually center Number
  dat$c_Num <- ifelse(dat$Number=='Numeric', -.5, .5)

  # CONDITION
  # make a factor out of Condition, as f_Cnd
  dat$f_Cnd <- factor(dat$Condition, levels=c(1,2,3,4), labels=c('Vg:Nm', 'Cr:Nm', 'Vg:Vb', 'Cr:Vb'))

@@

  # INSTRUCTION
  # add number of characters in the instruction # 29 30 34 36 38
  dat$nchar_instr = nchar(dat$Instruction)
  dat$nchar_instr_scaled = as.vector(scale(nchar(dat$Instruction), scale=TRUE))

@@

  # print to file a table with information about the design
  design_info <- unique(subset(dat, select=c(Item, Condition, Vagueness, Number, Quantity, Order, 
                                             Left, Mid, Right, Exp_Num, Bline_Num, Extr_Num, Exp_side, Bline_side, Extr_side,Instruction)))
  design.info <- design_info[order(design_info$Item, design_info$Condition, design_info$Quantity, design_info$Order),]
  row.names(design_info) <- NULL
  capture.output(  print.data.frame(design_info, row.names=F, print.gap=3, quote=F, right=F), file="design_info.table")

  # put dat in better column order
  dat <- subset(dat, 
                select = c(id, Subject, Trial, Condition, Order, Quantity, Vagueness, Number, 
                           Item, item_range_ratio, item_range_ratio_scaled, item_mean_ratio, item_mean_ratio_scaled,
                           c_Trl, s_Trl, c_Itm, c_Vag, c_Num, f_Cnd, c_Ord, c_Qty,
                           RT, RT_RecSqd, RT_Rec, RT_RecSqt, RT_log, RT_sqt, RT_raw, RT_sqd,
                           Exp_Num, Bline_Num, Extr_Num, Exp_side, Bline_side, Extr_side, response_num, response_side, response_category, Left, Mid, Right,
                           Instruction, nchar_instr
                ))

  # save dat as dat.Rda
  # This data set contains *all* trials 7680 including impossible trials and is mainly for graphs comparing different removals
  save(dat, file="dat.Rda")

  ####################################################
  # remove impossible trials from dat in new data dd #
  ####################################################

  # Throw out RT = 1 and RT = 59998, and RTprev = 1 and RTprev = 59998 
  # i.e., throw out sticky fingers and timeouts, 
  # and the trials that followed sticky fingers and timeouts 
  # since they were likely affected by unusual previous trials.

  # lose impossible trials
  dd <- dat
  dd$RT[dd$RT == 1 ] <- NA
  dd$RT[dd$RT == 59998 ] <- NA
  dd <- dd[complete.cases(dd),]
  row.names(dd) <- NULL

@@

  # number of higher-level cells in the design (abstracting over Order) = Item(4) * Number(2) * Vagueness(2) * Quantity(2) = 32
  # number of measurements in eaach cell = 8
  # 332 * 8 = 256
  # 256 * 30 = 7680

  dd$measurement=0
  dd$cell=0
  for (s in levels(dd$Subject)) {
    cellcount=0
    for (i in levels(dd$Item)) {
      for (n in levels(dd$Number)) {
        for (v in levels(dd$Vagueness)) {
          for (q in levels(dd$Quantity)) {
            measurementcount=0
            cellcount=cellcount+1
            for (t in dd[dd$Subject==s & dd$Item==i & dd$Number==n & dd$Vagueness==v & dd$Quantity == q, "Trial"]) {
              dd[dd$Subject==s & dd$Item==i & dd$Number==n & dd$Vagueness==v & dd$Quantity == q & dd$Trial==t, "cell"] <- cellcount
              measurementcount=measurementcount+1
              dd[dd$Subject==s & dd$Item==i & dd$Number==n & dd$Vagueness==v & dd$Quantity == q & dd$Trial==t, "measurement"] = measurementcount
            }
          }
        }
      }
    }    
  }

  # put dd in better column order
  dd <- subset(dd, 
               select = c(id, Subject, Trial, Condition, Order, Quantity, Vagueness, Number, 
                          Item, item_range_ratio, item_range_ratio_scaled, item_mean_ratio, item_mean_ratio_scaled,
                          c_Trl, s_Trl, c_Itm, c_Vag, c_Num, f_Cnd, c_Ord, c_Qty,
                          RT, RT_RecSqd, RT_Rec, RT_RecSqt, RT_log, RT_sqt, RT_raw, RT_sqd,
                          RTprev, RTprev_RecSqd, RTprev_Rec, RTprev_RecSqt, RTprev_log, RTprev_sqt, RTprev_raw, RTprev_sqd,
                          Exp_Num, Bline_Num, Extr_Num, Exp_side, Bline_side, Extr_side, response_num, response_side, response_category, Left, Mid, Right,
                          Instruction, nchar_instr,
                          cell, measurement
               ))

  # save dd
  save(dd, file="dd.Rda")
}
```

### 2018-08-02 experiments/C_exp_1/writeup/2017_submitted_to_springer/2017_submitted_to_springer.Rmd
massive restructuring Aug 2018

```{r load Libraries, message=FALSE, echo=FALSE}
library(knitr); library(Matrix); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions) 
```

@@

```{r e2-rtplot, fig.width=7, fig.height=3.5, echo=FALSE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, 
                                measurevar="RT_log", 
                                withinvars=c("Vagueness", "Number", "Item"), idvar="Subject")
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_logNormed, x=Item, group=Condition, fill=Vagueness)) +
  geom_line() +
  geom_errorbar(width=.2, aes(ymin=RT_logNormed-ci, ymax=RT_logNormed+ci)) +
  geom_point(size=2, col=1, aes(shape=Vagueness)) +
  scale_fill_grey(name="Vagueness", start=0, end=1) +
  scale_shape_manual(name="Vagueness", values=c(21,22)) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab(NULL) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="right",
        aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'),
        strip.background=element_blank(),
        axis.text.x = element_text(angle = 15)) +
  facet_grid(~Number)
rtplot
```

>>>>

```{r load Libraries, message=FALSE, echo=FALSE}
library(knitr); library(Matrix); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); library(kableExtra)
```

@@

```{r e2-rtplot, fig.width=7, fig.height=3.5, echo=TRUE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, 
                                measurevar="RT_log", 
                                withinvars=c("Vagueness", "Number", "Item"), idvar="Subject")
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))

rtdataplot1 %>% kable() %>% kable_styling(full_width = F, position = "left", font_size = 11)

rtplot=ggplot(rtdataplot1, aes(y=RT_logNormed, x=Item, group=Condition, fill=Vagueness)) +
  geom_line() +
  geom_errorbar(width=.2, aes(ymin=RT_logNormed-ci, ymax=RT_logNormed+ci)) +
  geom_point(size=2, col=1, aes(shape=Vagueness)) +
  scale_fill_grey(name="Vagueness", start=0, end=1) +
  scale_shape_manual(name="Vagueness", values=c(21,22)) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab(NULL) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="right",
        aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'),
        strip.background=element_blank(),
        axis.text.x = element_text(angle = 15)) +
  facet_grid(~Number)
rtplot
```

### 2018-08-02 experiments/C_exp_1/writeup/2018_tidy_version/e2_2018_analysis.Rmd
massive restructuring Aug 2018

@@

@@

>>>>

```{r}
ggplot(data=raw_data, aes(RT_log)) + geom_density() +xlim(6,11)+ylim(0,0.8)
```

@@

```{r}
ggplot(data=trim_data, aes(RT_log)) + geom_density()+xlim(6,11)+ylim(0,0.8)
```

```{r}
data.frame(obs=1:7680, raw=raw_data$RT_log, trim=c(trim_data$RT_log,rep(NA, times=239))) %>% 
  gather(key="type", value="value", raw, trim) %>%
  ggplot(aes(x=value, col=type)) + geom_density() + theme_bw() + theme(panel.grid = element_blank()) 
```

@@

rtdataplot1 %>% kable() %>% kable_styling(full_width = F, position = "left", font_size = 11)
